On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-09-13 Manuscript/manuscript.tex
Changed order of glmm and rank

The rest of this paper is organized as follows. Section~\ref{sec:Data} describes 
how data was collected and begins to detail the generalized linear mixed-effect 
(GLMM) model that is further developed in Section~\ref{sec:Methods}. The 
signed-rank test that analyzes reaction times for the same athletes across
different competitions is
also described in Section~\ref{sec:Methods}.  Section~\ref{sec:Results}
 provides the results of the two analyses and ends 
by questioning the reaction time barrier.  Lastly, Section~\ref{sec:concludingremarks}
discusses the impact and limitations of the paper.

@@

There are two types of data that are explored throughout this paper: data from
1999-2023 for every world championship, and data from athletes who competed in
the 2022 World Championships and another competition (either 2019 World 
Championships, 2023 World Championships or a 2022 national competition typically
held within three months of the 2022 World Championships).

The first data set is used for the GLMM analysis described in 
Section~\ref{sec:glmm}, while the second collection of data is used for the 
rank-based comparisons described in Section~\ref{sec:rank}.  This paper was
started shortly after the 2022 World Championships, but as the 2023 data has 
become available recently, we are pleased to include it in our analysis, and it
did not significantly change our results.

@@

%\eds{check these numbers? 0.099?}\of{resolved}

@@

The data described in Sections~\ref{sec:dataworld} and~\ref{sec:databeyond} were
analyzed with GLMM and rank-based methods, respectively.

@@

@@

The rank based methods described in Section~\ref{sec:rank}
to determine if the reaction times for athletes who had competed at other 
championships differed significantly from the 2022 World Championships.  This is
a two group comparison performed two times: once comparing 2019 World
Championships to 2022 World Championships and then comparing 2022 national
championships to the 2022 World Championships.

>>>>

The rest of this paper is organized as follows. Section~\ref{sec:Data} describes 
how data was collected and begins to detail the generalized linear mixed-effect 
(GLMM) model that is further developed in Section~\ref{sec:glmm}. The 
signed-rank test that analyzes reaction times for the same athletes across
different competitions is
also described in Section~\ref{sec:rank}.  Section~\ref{sec:Results}
 provides the results of the two analyses and ends 
by questioning the reaction time barrier.  Lastly, Section~\ref{sec:concludingremarks}
discusses the impact and limitations of the paper.

@@

There are two types of data that are explored throughout this paper.  For the
signed-rank tests described in section~\ref{sec:rank}, the data comes from 
athletes who competed in the 2022 World Championships and another competition 
(2019 World Championships, 2023 World Championships or 2022 national 
championships). For the GLMM described in section~\ref{sec:glmm}, data comes
from every world championship from 1999 to 2023. This paper was started shortly
after the 2022 World Championships, but as the 2023 data has become available 
recently, we are pleased to include it in both of our analyses, and it did not
significantly change our results.

@@

We also started to perform a similar analysis to compare the times of female 
athletes who competed at the 2019 and 2022 World Track and Field Championships,
however as our results were not significant, we decided to incorporate another
method to investigate the times at the 2022 World Championships and thus we
employ the GLMM, which looks at historical men's data to try to determine
whether Allen's time and disqualification are reasonable.

@@

The data described in Sections~\ref{sec:databeyond} and~\ref{sec:dataworld} were
analyzed with rank-based methods and a GLMM, respectively.

@@

The rank based methods described in Section~\ref{sec:rank}
to determine if the reaction times for athletes who had competed at other 
championships differed significantly from the 2022 World Championships.  This is
a two group comparison performed three times: comparing 2019 and 2022 World
Championships, comparing 2022 and 2023 World Championships, and comparing 2022 
national championships to the 2022 World Championships.

@@
